EpiExpert Crowd-Forecasting Performance Board

### 2021-02-15 evaluation/report-template.Rmd
update evaluation and app

```{r setup, include=FALSE}
library(covid.german.forecasts)
library(scoringutils)
library(dplyr)
library(DT)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```

@@

# Performance over time {.tabset}

>>>>

```{r setup, include=FALSE}
library(covid.german.forecasts)
library(scoringutils)
library(ggplot2)
library(dplyr)
library(DT)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE)
```

@@

# Performance and observations over time

Here you can see a visualisation of forecaster scores together next to the true observed values:

```{r forecast-and-scores, include = FALSE}
out <- NULL
out = c(out, knit_child(here::here("evaluation", "template-scores-and-truth-time.Rmd")))
```

# Ranks over time {.tabset}

### 2021-02-15 evaluation/template-ranking-over-time.Rmd
update evaluation and app

cat("\n\n ## model rank")
plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(low = "white", high = "coral")

@@

cat("\n\n ## standardised model rank")
plot <- score_heatmap(ranked_scores, metric = "standard_rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(high = "white", low = "coral")

>>>>

cat("\n\n## model rank\n\n")
plot <- score_heatmap(ranked_scores, metric = "rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(low = "white", high = "coral")

@@

cat("\n\n## standardised model rank\n\n")
plot <- score_heatmap(ranked_scores, metric = "standard_rank", 
                      x = "forecast_date",
                      facet_wrap_or_grid = "grid",
                      facet_formula = location_name ~ target_type) + 
  ggplot2::theme(legend.position = "bottom") +
    ggplot2::scale_fill_gradient(high = "white", low = "coral")
